Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-05-30 paper/comoving-followup.tex
note to self
summarize previous paper

\title{Co-moving stars in \textsl{Gaia DR1}:
       a catalog of genuine co-moving star pairs from low-resolution
       spectroscopic follow-up}

@@

\begin{abstract}
TODO:

\end{abstract}

@@

@@

Widely-separated co-moving stars are expected to form from the dissolution of
birth star clusters

@@

The wide-separation co-moving stars presented later in this work were originally
identified as candidate co-moving stars in a search of the \tgas\ catalog.

Target sample taken from ... Oh et al.

Briefly, ...

TGAS roughly XX\% complete to 200 pc with parallax SNR cut.

@@

@@

\subsection{Physical properties of genuine co-moving pairs}\label{sec:}

>>>>

\title{Co-moving stars in \textsl{Gaia DR1}:
       a catalog of genuine comoving star pairs from low-resolution
       spectroscopic follow-up}

@@

\begin{abstract}
% Context
Widely-separated, co-eval stars are [...] for studying the chemical homogeneity
of birth, calibrating stellar atmosphere models across a range of [..], and for
modeling the Galactic tidal field.
Previous work using Hipparcos + literature RVs -> a few hundred genuine pairs
out to 8 pc.
% Aims
Identified candidate pairs using the Tycho-Gaia Astrometric Solution catalog,
Gaia DR1.
Want to identify genuinely dynamically associated pairs for future
high-resolution followup
% Methods
Low-resolution spectrograph to measure relative radial velocities to identify
genuine pairs.
% Results
Of the XX pairs observed, we find YY ...
% Conclusions
Gaia DR2 -> how many do we expect?
\end{abstract}

@@

comoving not wide binary (don't know if they are bound)

@@

Widely-separated comoving stars are expected to form from the dissolution of
birth star clusters

@@

In previous work, we have identified a sample of high-confidence, candidate
comoving star pairs (\citealt{Oh:2017}) using only astrometric information from
the \tgas\ catalog (\citealt{tgas}).
These comoving pairs were selected using a cut on a marginalized likelihood
ratio computed for all nearly co-spatial pairs of stars.
For a full description of the selection method, see \citealt{Oh:2017}.
Briefly, likelihood 1, $L_1$, considers a model in which the full-space
velocities of each star in the pair are identical and sampled from a disk-like,
Sun-relative velocity distribution, and likelihood 2, $L_2$, considers a model
in which the full-space velocities of each star were drawn independently from
the same velocity distribution used above; the likelihood ratio was taken as
$L_1/L_2$.
After a parallax signal-to-noise cut ($\pi/\sigma_\pi > 8$), we compute the
likelihood ratio for all stars within $10~\pc$ of each target star from the
\tgas\ catalog.
The likelihoods appropriately take into account the reported covariances and
uncertainties between the astrometric measurements in the \tgas\ catalog and
naturally handle geometric or projection effects in comparing spherical velocity
components for star pairs separated by large angles on the sky.
After applying a conservative cut on the likelihood ratio motivated by computing
the same likelihood ratio for random pairings of stars, we find 13,058
comoving star pairs with physical separations between $1000~\au$ and $10~\pc$.
Of these pairs, there are 10,606 unique sources, implying that a significant
fraction of the identified pairs are members of larger groups.

TGAS $\approx$90\% complete to 200 pc with parallax SNR cut (\citealt{Bovy:2017}).

@@

TODO:
- Plot of magnitude of 3d velocity difference vs. 3d separation (inferred).

@@

\subsection{Physical properties of genuine comoving pairs}\label{sec:}
